### 2021-07-10 src/paper/model/estimated_parameters.tex
Move plot of other multiplier to estimated parameter section.

Moreover, we estimate nine different multipliers that reflect how strongly other
contacts are reduced over time. The dates at which we switch between the multipliers
usually coincides with policy changes and is not determined from the data. The only
exception to this are slight adjustments to parameters to incorporate lockdown fatigue
(towards the end of a lockdown period) or precautionary contact reductions (in times
of high incidences right before a lockdown is enacted).

>>>>

Moreover, we estimate nine different multipliers that reflect how strongly other
contacts are reduced over time. The dates at which we switch between the multipliers
usually coincides with policy changes and is not determined from the data. The only
exception to this are slight adjustments to parameters to incorporate lockdown fatigue
(towards the end of a lockdown period) or precautionary contact reductions (in times
of high incidences right before a lockdown is enacted). The estimated other multipliers
are also depicted in Figure~\ref{fig:other_multiplier}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/other_multiplier}
    \caption{Share of Pre-Pandemic Other Contacts Taking Place with Infection Potential}
    \label{fig:other_multiplier}
    \floatfoot{\noindent \textit{Note:} Values of the other multiplier. All values are
    estimated via the method of simulated moments. The rationale behind each switching
    point is described in Table~\ref{tab:estimated_params}}
\end{figure}
